---
title: "Analysis Summary"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  bookdown::html_document2:
    number_sections: no
    fig_caption: true
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
editor_options:
  chunk_output_type: inline
---

```{r setup knit, include=FALSE}
knitr::opts_chunk$set(
	fig.align = "center",
	fig.pos = "H",
	fig.width = 10,
	fig.height = 10,
	message = FALSE,
	warning = FALSE,
	external = TRUE,
	echo = TRUE
)

library(tidyverse)
library(magrittr)
library(plotly)
library(fastDummies)
library(ggalt)
library(reshape2)
library(RColorBrewer)
library(kableExtra)
library(ggsci)

library(cluster)
library(factoextra)
library(mclust)
library(neuralnet)
library(dendextend)  # color dendrogram 

source("../R script/functions.R")
```



```{r load and clean data}
## Data Cleaning

# load raw data files
data = read.csv("../data/filledDatabase111119NUMONLY.csv")

# clean data 
data = clean_data(data)

# separate compound and group_cate from the predictors
compound = data$Compound
group_cat = data$GroupCat
X = data$X

group_cat_text = paste("Grp", group_cat)
data = select(data, -c("Compound","GroupCat","X"))
```

## Hierarchical model 

```{r}
data_matrix = data %>% as.matrix()

model_complete = hclust( dist(data_matrix), method = "complete" )

## use elbow ... etc to decide K
```

```{r}
summary(X) %>% 
  as.data.frame() %>%
  set_colnames("Frequency") %>%
  rownames_to_column("X") %>%
  arrange(desc(Frequency)) %>% 
  t() %>%
  kable(caption = "Frequency table for cluster X of data version 11/11/19") %>% 
  kable_styling(bootstrap_options = "striped")
```










## Cluster O

### PCA circle

```{r fig.cap="Cluster O: vectors of predictors in the space of PC1 and PC2"}
# data slicing 
rows_to_take = X == "O"

subset = data[rows_to_take, ] 
compound_sub = compound[rows_to_take]
group_cat_sub = group_cat[rows_to_take]
group_cat_text_sub = group_cat_text[rows_to_take]

# variables in PC space
fviz_pca_var(
  prcomp(subset, scale = TRUE),
  col.var = "contrib", # Color by contributions to the PC
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     # Avoid text overlapping
)
```

### Compounds in space of PC's

```{r fig.cap="Cluster O: compounds in the space of the first two PC's"}
set_color = c("#0071C3","#DE501A","#EEB020","#7E2E8E","#79AC2C","#4DBDF7","#A51331") %>% 
  rep(10)

# extract three two PC's
data_pca = get_pc_space(subset, k = 3) %>% scale()

# plot
data.frame(Compound = compound_sub, GroupCat = group_cat_text_sub, data_pca) %>%
  ggplot(aes(x=PC1, y=PC2, color = GroupCat)) +
  geom_point(aes(color = GroupCat), size = 2, alpha = 0.4) +
  geom_text(aes(label=Compound, color=GroupCat), size = 3) +
  scale_color_manual(values=set_color) +
  scale_fill_manual(values=set_color) +
  scale_shape_manual(values=1:11) +
  theme_minimal()
```



### PCA biplot

```{r fig.cap="Cluster O: compounds and predictor vectors in the space of the first two PC's"}
rownames(subset) = make.names(compound_sub, unique=TRUE)
fit <- prcomp(subset, scale = TRUE)
fviz_pca_biplot(fit, aesx = c(1,2),
                # individual
                label = "var", labelsize = 4,
                geom = c("point","text"), fill.ind = group_cat_text_sub, alpha.ind = 0.7,
                pointsize = 2, pointshape = 21, palette = set_color[1:11],
                # variable
                col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel=TRUE) +
  labs(fill = "Group Cat", color = "Contrib")
```




## Cluster F

### PCA circle

```{r fig.cap="Cluster F: vectors of predictors in the space of PC1 and PC2"}
# data slicing 
rows_to_take = X == "F"

subset = data[rows_to_take, ]
compound_sub = compound[rows_to_take]
group_cat_sub = group_cat[rows_to_take]
group_cat_text_sub = group_cat_text[rows_to_take]

# variables in PC space
fviz_pca_var(
  prcomp(subset, scale = TRUE),
  col.var = "contrib", # Color by contributions to the PC
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     # Avoid text overlapping
)
```

### Compounds in space of PC's

```{r fig.cap="Cluster F: compounds in the space of the first two PC's"}
# extract three two PC's
data_pca = get_pc_space(subset, k = 3) %>% scale()

# plot
data.frame(Compound = compound_sub, GroupCat = group_cat_text_sub, data_pca) %>%
  ggplot(aes(x=PC1, y=PC2, color = GroupCat)) +
  geom_point(aes(color = GroupCat), size = 2, alpha = 0.4) +
  geom_text(aes(label=Compound, color=GroupCat), size = 3) +
  scale_color_manual(values=set_color) +
  scale_fill_manual(values=set_color) +
  scale_shape_manual(values=1:11) +
  theme_minimal()
```

### PCA biplot

```{r fig.cap="Cluster F: compounds and predictor vectors in the space of the first two PC's"}
rownames(subset) = make.names(compound_sub, unique=TRUE)
fit <- prcomp(subset, scale = TRUE)
fviz_pca_biplot(fit, aesx = c(1,2),
                # individual
                label = "var", labelsize = 4,
                geom = c("point","text"), fill.ind = group_cat_text_sub, alpha.ind = 0.7,
                pointsize = 2, pointshape = 21, palette = set_color[1:11],
                # variable
                col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel=TRUE) +
  labs(fill = "Group Cat", color = "Contrib")
```


## Cluster Cl

### PCA circle

```{r fig.cap="Cluster Cl: vectors of predictors in the space of PC1 and PC2"}
# data slicing 
rows_to_take = X == "Cl"

subset = data[rows_to_take, ]
compound_sub = compound[rows_to_take]
group_cat_sub = group_cat[rows_to_take]
group_cat_text_sub = group_cat_text[rows_to_take]

# variables in PC space
fviz_pca_var(
  prcomp(subset, scale = TRUE),
  col.var = "contrib", # Color by contributions to the PC
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     # Avoid text overlapping
)
```

### Compounds in space of PC's

```{r fig.cap="Cluster Cl: compounds in the space of the first two PC's"}
# extract three two PC's
data_pca = get_pc_space(subset, k = 3) %>% scale()

# plot
data.frame(Compound = compound_sub, GroupCat = group_cat_text_sub, data_pca) %>%
  ggplot(aes(x=PC1, y=PC2, color = GroupCat)) +
  geom_point(aes(color = GroupCat), size = 2, alpha = 0.4) +
  geom_text(aes(label=Compound, color=GroupCat), size = 3) +
  scale_color_manual(values=set_color) +
  scale_fill_manual(values=set_color) +
  scale_shape_manual(values=1:11) +
  theme_minimal()
```

### PCA biplot

```{r fig.cap="Cluster Cl: compounds and predictor vectors in the space of the first two PC's"}
rownames(subset) = make.names(compound_sub, unique=TRUE)
fit <- prcomp(subset, scale = TRUE)
fviz_pca_biplot(fit, aesx = c(1,2),
                # individual
                label = "var", labelsize = 4,
                geom = c("point","text"), fill.ind = group_cat_text_sub, alpha.ind = 0.7,
                pointsize = 2, pointshape = 21, palette = set_color[1:11],
                # variable
                col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel=TRUE) +
  labs(fill = "Group Cat", color = "Contrib")
```


## Cluster Br

### PCA circle

```{r fig.cap="Cluster Br: vectors of predictors in the space of PC1 and PC2"}
# data slicing 
rows_to_take = X == "Br"

subset = data[rows_to_take, ]
compound_sub = compound[rows_to_take]
group_cat_sub = group_cat[rows_to_take]
group_cat_text_sub = group_cat_text[rows_to_take]

# variables in PC space
fviz_pca_var(
  prcomp(subset, scale = TRUE),
  col.var = "contrib", # Color by contributions to the PC
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     # Avoid text overlapping
)
```

### Compounds in space of PC's

```{r fig.cap="Cluster Br: compounds in the space of the first two PC's"}
# extract three two PC's
data_pca = get_pc_space(subset, k = 3) %>% scale()

# plot
data.frame(Compound = compound_sub, GroupCat = group_cat_text_sub, data_pca) %>%
  ggplot(aes(x=PC1, y=PC2, color = GroupCat)) +
  geom_point(aes(color = GroupCat), size = 2, alpha = 0.4) +
  geom_text(aes(label=Compound, color=GroupCat), size = 3) +
  scale_color_manual(values=set_color) +
  scale_fill_manual(values=set_color) +
  scale_shape_manual(values=1:11) +
  theme_minimal()
```

### PCA biplot

```{r fig.cap="Cluster Br: compounds and predictor vectors in the space of the first two PC's"}
rownames(subset) = make.names(compound_sub, unique=TRUE)
fit <- prcomp(subset, scale = TRUE)
fviz_pca_biplot(fit, aesx = c(1,2),
                # individual
                label = "var", labelsize = 4,
                geom = c("point","text"), fill.ind = group_cat_text_sub, alpha.ind = 0.7,
                pointsize = 2, pointshape = 21, palette = set_color[1:11],
                # variable
                col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel=TRUE) +
  labs(fill = "Group Cat", color = "Contrib")
```


## Cluster I

### PCA circle

```{r fig.cap="Cluster I: vectors of predictors in the space of PC1 and PC2"}
# data slicing 
rows_to_take = X == "I"

subset = data[rows_to_take, ]
compound_sub = compound[rows_to_take]
group_cat_sub = group_cat[rows_to_take]
group_cat_text_sub = group_cat_text[rows_to_take]

# variables in PC space
fviz_pca_var(
  prcomp(subset, scale = TRUE),
  col.var = "contrib", # Color by contributions to the PC
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     # Avoid text overlapping
)
```

### Compounds in space of PC's

```{r fig.cap="Cluster I: compounds in the space of the first two PC's"}
# extract three two PC's
data_pca = get_pc_space(subset, k = 3) %>% scale()

# plot
data.frame(Compound = compound_sub, GroupCat = group_cat_text_sub, data_pca) %>%
  ggplot(aes(x=PC1, y=PC2, color = GroupCat)) +
  geom_point(aes(color = GroupCat), size = 2, alpha = 0.4) +
  geom_text(aes(label=Compound, color=GroupCat), size = 3) +
  scale_color_manual(values=set_color) +
  scale_fill_manual(values=set_color) +
  scale_shape_manual(values=1:11) +
  theme_minimal()
```

### PCA biplot

```{r fig.cap="Cluster I: compounds and predictor vectors in the space of the first two PC's"}
rownames(subset) = make.names(compound_sub, unique=TRUE)
fit <- prcomp(subset, scale = TRUE)
fviz_pca_biplot(fit, aesx = c(1,2),
                # individual
                label = "var", labelsize = 4,
                geom = c("point","text"), fill.ind = group_cat_text_sub, alpha.ind = 0.7,
                pointsize = 2, pointshape = 21, palette = set_color[1:11],
                # variable
                col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel=TRUE) +
  labs(fill = "Group Cat", color = "Contrib")
```



















```{r}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = FALSE,
	eval = FALSE
)
```

## PCA

### PCA circle 

```{r fig.cap="Vectors of predictors in the space of PC1 and PC2"}
fviz_pca_var(
  prcomp(data, scale = TRUE),
  col.var = "contrib", # Color by contributions to the PC
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     # Avoid text overlapping
)
```

### PCA importance

Here we choose first 17 PC for further analysis.

```{r pca}
# print out the cumulative proportions for first k PC's
print_pca_importance(data, k = 20)

# transform data to a new space
data_pca = get_pc_space(data, k = 17) %>% scale()
```

### Compounds in space of PC's

```{r fig.cap="Compounds in the space of the first two PC's"}
set_color = c("#0071C3","#DE501A","#EEB020","#7E2E8E","#79AC2C","#4DBDF7","#A51331") %>% 
  rep(10)

data.frame(Compound = compound, GroupCat = group_cat_text, data_pca) %>%
  ggplot(aes(x=PC1, y=PC2, color = GroupCat)) +
  geom_point(aes(color = GroupCat), size = 2, alpha = 0.4) +
  geom_text(aes(label=Compound, color=GroupCat), size = 3) +
  scale_color_manual(values=set_color) +
  scale_fill_manual(values=set_color) +
  scale_shape_manual(values=1:11) +
  theme_minimal()
```

### PCA biplot

```{r fig.cap="PCA biplot (compounds and predictor vectors in the space of the first two PC's)"}
rownames(data) = make.names(compound, unique=TRUE)
fit <- prcomp(data, cor=TRUE)
fviz_pca_biplot(fit, aesx = c(1,2),
                # individual
                label = "var", labelsize = 4,
                geom = c("point","text"), fill.ind = group_cat_text, alpha.ind = 0.7,
                pointsize = 2, pointshape = 21, palette = set_color[1:11],
                # variable
                col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel=TRUE) +
  labs(fill = "Group Cat", color = "Contrib")
```



### Cubic vs Tilted

#### 2D

```{r fig.height=5, fig.cap="Cubic and Tilted in the space of the first two PC's"}
data.frame(Compound = compound, GroupCat = group_cat_text, data_pca) %>%
  filter(GroupCat %in% c("Grp 3","Grp 5")) %>%
  ggplot(aes(x=PC1, y=PC2, color = GroupCat)) +
  # geom_point(aes(color = GroupCat), size = 4, alpha = 0.4) +
  geom_text(aes(label=Compound, color=GroupCat), size = 3, alpha = 0.7) +
  scale_color_manual(values=set_color) +
  scale_fill_manual(values=set_color) +
  scale_shape_manual(values=1:11) +
  theme_minimal()
```

#### 3D

```{r fig.cap="Cubic and Tilted in the space of the first two PC's"}
data.frame(Compound = compound, GroupCat = group_cat_text, data_pca) %>%
  filter(GroupCat %in% c("Grp 3","Grp 5")) %>%
  droplevels() %>%
  plot_ly(x = ~PC1, y = ~PC2, z = ~PC3, color = ~GroupCat, text = ~Compound, colors = set_color[1:2]) %>%
  add_markers(marker=list(size = 7, opacity = 0.6)) %>%
  layout(scene = list(xaxis = list(title = 'PC1'),
                      yaxis = list(title = 'PC2'),
                      zaxis = list(title = 'PC3')),
         title = "Cubic and Titled in the space of PC1, PC2, PC3")
```

#### Biplot

```{r}
fit = prcomp(data_biplot, cor=TRUE)

new_color = c()

for(i in 1:11){
  group_tag = levels(as.factor(group_cat_text))[i]
  if(group_tag %in% c("Grp 3","Grp 5")){
    new_color[i] = set_color[i+2]
  }else{
    new_color[i] = "white"
  }
}

fviz_pca_biplot(fit, aesx = c(1,2),
                # individual
                label = "var", labelsize = 4,
                geom = c("point","text"), fill.ind = group_cat_text, col.ind = "white", alpha.ind = 0.7,
                pointsize = 2, pointshape = 21, palette = new_color,
                # variable
                col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel=TRUE) +
  labs(fill = "Group Cat", color = "Contrib", title = "PCA biplot - Cubic and Tilted")
```

```{r}
# data_3 = data[group_cat_text %in% c("Grp 3"),] %>% mutate(GroupCat = "Grp 3")
# data_5 = data[group_cat_text %in% c("Grp 5"),] %>% mutate(GroupCat = "Grp 5")
# 
# data_3_5 = rbind(data_3, data_5)
# ggplot(melt(data_3_5[,c(49:59,60)], id.vars="GroupCat"), aes(value)) + 
#   geom_histogram(bins = 20, aes(fill=GroupCat), position = "dodge", color = "grey", size = 0.1) + 
#   facet_wrap(~variable, scales = 'free_x') +
#   scale_fill_manual(values = set_color) +
#   theme_bw()
```


## K-means 

### k = 2 

```{r}
kmean_results = get_kmeans_results(data_pca, k = 2)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 3

```{r}
kmean_results = get_kmeans_results(data_pca, k = 3)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 4

```{r}
kmean_results = get_kmeans_results(data_pca, k = 4)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 5 

```{r}
kmean_results = get_kmeans_results(data_pca, k = 5)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 6

```{r}
kmean_results = get_kmeans_results(data_pca, k = 6)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 7

```{r}
kmean_results = get_kmeans_results(data_pca, k = 7)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 8 

```{r}
kmean_results = get_kmeans_results(data_pca, k = 8)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 9 

```{r}
kmean_results = get_kmeans_results(data_pca, k = 9)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 10 

```{r}
kmean_results = get_kmeans_results(data_pca, k = 10)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 11

```{r}
kmean_results = get_kmeans_results(data_pca, k = 11)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 12 

```{r}
kmean_results = get_kmeans_results(data_pca, k = 12)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 13

```{r}
kmean_results = get_kmeans_results(data_pca, k = 13)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```


### k = 14 

```{r}
kmean_results = get_kmeans_results(data_pca, k = 14)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 15

```{r}
kmean_results = get_kmeans_results(data_pca, k = 15)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 16

```{r}
kmean_results = get_kmeans_results(data_pca, k = 16)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 20

```{r}
kmean_results = get_kmeans_results(data_pca, k = 20)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 24

```{r}
kmean_results = get_kmeans_results(data_pca, k = 24)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```

### k = 25

```{r}
kmean_results = get_kmeans_results(data_pca, k = 25)
get_kmeans_visual_2D(kmean_results)
```

```{r fig.height=5}
get_kmeans_histogram(kmean_results)
```






```{r kmeans visual} 
### explore k visually

# choose the number of clusters to explore
# k = 4
# 
# # build a model for kmeans
# kmean_results = get_kmeans_results(data_pca, k = k)
# 
# # generate 2D visual for this k 
# get_kmeans_visual_2D(kmean_results)
# 
# # histogram matlab 
# get_kmeans_histogram(kmean_results)

# generate 3D visual for this k
# get_kmeans_visual_3D(kmean_results)
```



```{r kmeans save results}
### save results 

# choose k to save
# k = c(2:25)

# save the result as csv
# save_kmeans_results(data, data_pca, k)
```


```{r}
knitr::opts_chunk$set(
	fig.width = 10,
	fig.height = 5
)
```


## Mclust

Based on a criterion *BIC*, we choose a Gaussian mixture model with 3 components. 

```{r mclust visual}
### mclust visuals

# build a model for mclust
model = get_mclust_model(data_pca)

# print summary table of the model
summary(model)

# generate 2D visual for mclust
get_mclust_visual_2D(model)

# histogram matlab 
get_mclust_histogram(model)

# generate 3D visual for mclust
# get_mclust_visual_3D(model)
```



```{r mclust save results}
### save results 

# save_mclust_results(data, data_pca, compound, group_cat)
```


## Neural Nets

- Classify all data points to 6 largest groups
- 4-hidden-layer model with leave-one-out achieves classification rate 54% 

<!-- ```{r} -->
<!-- group_cat %>% check_missing() -->
<!-- data_pca_scaled = scale(data_pca) %>% as.data.frame() -->
<!-- ``` -->

<!-- ### K = 3 -->

<!-- ```{r} -->
<!-- group_cat_dummy = dummy_group_cat(group_cat, k = 3) -->
<!-- get_nn_cv_rate(group_cat_dummy, data_pca_scaled) %>% mean() -->
<!-- ``` -->

<!-- ### K = 4 -->

<!-- ```{r} -->
<!-- group_cat_dummy = dummy_group_cat(group_cat, k = 4) -->
<!-- get_nn_cv_rate(group_cat_dummy, data_pca_scaled) %>% mean() -->
<!-- ``` -->x

<!-- ### K = 5 -->

<!-- ```{r} -->
<!-- group_cat_dummy = dummy_group_cat(group_cat, k = 5) -->
<!-- get_nn_cv_rate(group_cat_dummy, data_pca_scaled) %>% mean() -->
<!-- ``` -->

<!-- ### K = 6 -->

<!-- ```{r} -->
<!-- group_cat_dummy = dummy_group_cat(group_cat, k = 6) -->
<!-- get_nn_cv_rate(group_cat_dummy, data_pca_scaled) %>% mean() -->
<!-- ``` -->

<!-- ### K = 7 -->

<!-- ```{r} -->
<!-- group_cat_dummy = dummy_group_cat(group_cat, k = 7) -->
<!-- get_nn_cv_rate(group_cat_dummy, data_pca_scaled) %>% mean() -->
<!-- ``` -->

<!-- ### K = 8 -->

<!-- ```{r} -->
<!-- group_cat_dummy = dummy_group_cat(group_cat, k = 8) -->
<!-- get_nn_cv_rate(group_cat_dummy, data_pca_scaled) %>% mean() -->
<!-- ``` -->

<!-- ### K = 9 -->

<!-- ```{r} -->
<!-- group_cat_dummy = dummy_group_cat(group_cat, k = 9) -->
<!-- get_nn_cv_rate(group_cat_dummy, data_pca_scaled) %>% mean() -->
<!-- ``` -->





```{r}
# # check any missing values in chem group
# group_cat %>% check_missing()
# 
# # dummy first k chem group
# group_cat_dummy = dummy_group_cat(group_cat, k = 5)
# 
# # normalize data_pca
# data_pca_scaled = scale(data_pca) %>% as.data.frame()
# 
# # compute cv classification rate
# get_nn_cv_rate(group_cat_dummy, data_pca_scaled) %>% mean()

# build a model for neural nets
# model = get_nn_model(group_cat_dummy, data_pca_scaled)

# plot neural nets
# library(devtools)
# source_url('https://gist.githubusercontent.com/fawda123/7471137/raw/466c1474d0a505ff044412703516c34f1a4684a5/nnet_plot_update.r')
# plot.nnet(model)

# save nn results 
# save_nn_results(model, compound, group_cat, data, names(group_cat_dummy))

# save model weights (layers = 20,10,5)
# data.frame(weight = model$result.matrix) %>% 
#   rownames_to_column() %>% 
#   filter(between(row_number(), 4, n())) %>% 
#   separate(rowname, c("node_in","node_out"), sep = ".to.") %>%
#   write.csv("../result/nn weights.csv", row.names = FALSE)
```



```{r}
### explore for k 

# k = c(3:11)
# 
# dummy = list()
# for(i in 1:length(k)){
#   dummy[[i]] = repeat_B(k = k[i])
# }
# 
# data.frame(dummy) %>% 
#   set_colnames(paste("k=", k, sep="")) %>%
#   reshape2::melt() %>%
#   ggplot(aes(x = value)) +
#   geom_histogram(bins = 30) +
#   labs(x="Classification Rate", y="Frequency") +
#   theme_bw() + coord_flip() +
#   facet_grid(~variable)


# data.frame(dummy) %>% set_colnames(paste("k=", k, sep="")) %>%
#   write.csv("../result/nn class rate.csv", row.names = FALSE)
```



